\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{nopageno}
\title{Brief Article}
\author{The Author}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
%\maketitle
%\section{}
%\subsection{}

\begin{center}
{\bf Midterm}
\end{center}

Name: 

ID: 

All answers shall be justified properly to get full credits. Each question counts 10 points.
\vspace{.2in}

Throughout this exam, let 
$A = 
\begin{bmatrix}
1 & 1 & 0& 0\\
1 & 1 & 1 & 2
\end{bmatrix}
$, 
$B = \begin{bmatrix}
0 & -2 \\
2 & 0
\end{bmatrix}
$,
and 
$
v
 = 
\begin{bmatrix}
1\\
3
\end{bmatrix}
$.
\vspace{.2in}


\begin{enumerate}
\item  Consider the matrix equation $Ax = v$. 
\begin{enumerate}
\item Write its augmented matrix.
\vspace{.5in}
\item Find its reduced row echelon form.
\vspace{.5in}
\vspace{.5in}
\vspace{.5in}
\item  Write its solution set into a parametric vector form, if there is any.
\vspace{.5in}
\vspace{.5in}
\vspace{.5in}
\end{enumerate}

\item  %Write the parametric vector form of homogeneous equation $Ax = 0$.
Is the transformation defined by $Tx = Ax$
a one-to-one or onto mapping?

\vspace{.5in}
\vspace{.5in}


\newpage
\item We denote by $A = [a_1, a_2, a_3, a_4]$, where $a_1$, $a_2$, $a_3$, $a_4$ are column vectors of $A$.
\begin{enumerate}
\item Does  $a_3$ belong to the span generated by $a_1$ and $a_2$?
\vspace{.5in}
\vspace{.5in}
  \item
Are vectors $\{a_1, a_2, a_3, a_4\}$ independent?
\vspace{.5in}
\vspace{.5in}
\vspace{.5in}
\item
 Write a parametric vector form for the line going through $a_1$ and $a_2$.
 \vspace{.5in}
 \vspace{.5in}
 \vspace{.5in}
\end{enumerate}



\item
\begin{enumerate}
\item Compute $v^TAv$, $v^TBv$, respectively, whenever they are well defined.
\vspace{.5in}
\vspace{.5in}
\item
Compute $BA$, $BAB$, respectively, whenever they are well defined.

\vspace{.5in}
\vspace{.5in}
\item Compute $B^{9}A$  whenever they are well defined.
\vspace{.5in}
\vspace{.5in}
\vspace{.5in}
\end{enumerate}



\end{enumerate}


\end{document}  